%!TEX TS-program = xelatex
\documentclass[print]{cv}

\begin{document}
\header{Rocco}{ Galluzzo}
{Fullstack Web Developer}

\begin{aside}%
\section{contacts}
C/da San Pietro 4
S. Giovanni di G.
89040 RC - Italy\par\smallskip%
+39347500******
\href{mailto:rocco@galluzzo.me}{rocco@galluzzo.me}
\section{online}
\href{http://rocco.galluzzo.me}{http://rocco.galluzzo.me}
         \par\smallskip%
         \href{https://github.com/byterussian}{GitHub://byterussian}
         \href{http://www.linkedin.com/in/roccogalluzzo}{Linkedin://roccogalluzzo}
         \section{languages}
         Italian(Mothertongue)
 \smallskip%
         English(B2, C1)
         \section{programming}
          \textbf{Ruby}
         (Rails, Sinatra, Grape)
 \smallskip%
          \textbf{JavaScript}
         (jQuery, Angular, React)
 \smallskip%
          \textbf{CSS3} \&  \textbf{HTML5}
         (LESS, SASS)
 \smallskip%
          \textbf{Python}
         (Django, Flask)
 \smallskip%
          \textbf{Others}
         Scala, C, PHP, Go Lang
         \end{aside}

         \section{summary}
         Fullstack web developer with over six years of professional experience. Focus on sustainable web application architecture
         using Ruby on Rails, Angular.js, jQuery and responsive HTML/CSS.

         Also I have excellent knowledge of TDD, version control software(Git, Mercurial), SQL(MySQL, PostgreSQL) and NoSQL(Redis, MondoDB) databases.
         \section{education}

         \begin{entrylist}
	         \entry
         {2002-2007}
         {Secondary School}
         {IPSIA, Siderno RC}
         {Electronics. 80/100}

         \entry
         {2013}
         {Functional Programming Principles in Scala}
         {Coursera/École Polytechnique de Lausanne}
         {}

     \entry
         {2013}
         {Machine Learning Course}
         {Coursera/Stanford University}
         {}

     \entry
         {2014}
         {Principles of Reactive Programming}
         {Coursera/École Polytechnique de Lausanne}
         {}

         \end{entrylist}

         \section{experience}

         \begin{entrylist}
        \entry
         {20-11 2014}
         {\href{http://mailup.com}{MailUp S.p.A.}}
         {Freelance Job}
         {\emph{I've contributed to the development of the REST API gem and of the MailUp Shopify App.}}
         \entry
         {01-10 2013}
         {\href{http://www.upandsell.me}{Up\&Sell.Me}}
         {Co-founder \& Developer}
         {\emph{SaaS startup for selling digital products online. I've developed alone both the backend(with Rails) and the front end.}}
         \entry
         {01-09 2007}
         {Freelance}
         {Freelance Job}
         {\emph{Development of PHP scripts, plugins for Wordpress and Joomla and intranet apps for many companies.}}
         \end{entrylist}

         \section{interests}

         Books, electronics, UX\&UI, startup world, TV series, rock music, motorcycles.

         \end{document}
